---
title: "p8105 hw6 solutions"
author: "Shuhong Xiang"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(modelr)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 12, 
  fig.height = 8,
	fig.path='Figs/',
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

tart with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Problem 2

Load and clean the dataset:
```{r}
birthweight <- read_csv("data/birthweight.csv")

birthweight_df = 
 birthweight%>%
 janitor::clean_names() %>%
 mutate(babysex = 
    factor(
     case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"
     )),
   frace = factor(
     case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other"
     )),
   malform = factor(
    case_when(
     malform == 0 ~ "absent",
     malform == 1 ~ "present"
    )),
   mrace = factor(
    case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      mrace == 8 ~ "Other"     
    ))
   )
```

#### Fist, I want to look at the overall model:

```{r}
birthweight_df %>%
 lm(bwt ~ . , data = .) %>%
 broom::tidy()
```

#### Besed on the coeffienct above, the both-way stepwise variable selction is used:

```{r}
model_stepwise = lm(bwt ~ . , data = birthweight_df) 
step(model_stepwise, direction = "both") 
```

According to the results of step-wise variable selection, then I choose babysex, bhead, blength, mrace and parity as variable in my model.

Thus, build my model based on the five variables:

```{r}
my_model = lm(formula = bwt ~ babysex + bhead + blength + mrace + parity, data = birthweight_df)
broom::glance(my_model)
```

Plot residuals against fitted values of my model: 

```{r}
plot_my_model = 
  birthweight_df %>%  
  modelr::add_residuals(my_model) %>% 
  modelr::add_predictions(my_model) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  geom_smooth(formula = y ~ x, method = "lm") + 
  labs(
    title = "Plot of Model Residuals against Fitted Values",
    x = "Fitted Values",
    y = "Residuals"
  )

plot_my_model
```


### Problem 3

Load the dataset:
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

#### Set up bootstrap and show the results of bootstrap:

```{r}
set.seed(1)
bootstrap_weather = 
 modelr::bootstrap(weather_df, n = 5000, id = "id") %>%
 mutate(
  lm_model = map(strap, ~lm(tmax ~ tmin, data = .x) ),
  lm_model_summary = map(lm_model, broom::tidy),
  lm_model_glance = map(lm_model, broom::glance)
  ) %>% 
  unnest(lm_model_summary,lm_model_glance) %>% 
  select(id, term, estimate, r.squared)

bootstrap_weather %>% 
 head() %>% 
 knitr::kable()
```

#### Plot the distribution of r^2 and 2.5% and 97.5% quantiles to provide a 95% confidence interval: 

```{r}
bootstrap_weather %>%
  ggplot(aes(x = r.squared)) +
  geom_density()+
  labs(
    title = "The Distribution of r^2",
    x = "r^2 value"
  )
```

```{r}
bootstrap_weather %>%
  summarize(
    Estimate = "r^2",
    CI_lower = quantile(r.squared, 0.025), 
    CI_upper = quantile(r.squared, 0.975)
    ) %>% 
 knitr::kable(caption = "95% CI of r^2")
```

#### Calculate the value of log(beta_0 * beta_1) and plot the distribution. Then, 2.5% and 97.5% quantiles to provide a 95% confidence interval:

```{r}
bootstrap_weather %>%
  select(id, term, estimate) %>%
  pivot_wider(names_from = term,
              values_from = estimate) %>%
  mutate(
   log_value = log(tmin * `(Intercept)`)
   ) %>%
  ggplot(aes(x = log_value)) +
  geom_density() +
  labs(
    title = "Distribution of log(beta_0 * beta_1)",
    x = "log(beta_0 * beta_1)"
  )
```

```{r}
bootstrap_weather %>%
  select(id, term, estimate) %>%
  pivot_wider(names_from = term,
              values_from = estimate) %>%
  mutate(
   log_value = log(tmin * `(Intercept)`)
   ) %>%
  summarise(
    Estimate = "log(beta_0 * beta_1)",
    CI_lower = quantile(log_value, 0.025), 
    CI_upper = quantile(log_value, 0.975)
    ) %>% 
 knitr::kable(caption = "95% CI of log(beta_0 * beta_1)")
```

From the graphs pf distribution above, we can see the distribution of R square is basically normal and mean is about 0.91. Besides, the the plot of log(beta_0 * beta_1) shows that the value of the value of log(beta_0 * beta_1) is also normally distributed around the 2.03.